% -------------------------------------------------------- %
% Gabarit d'article pour la revue L'Actualité économique / %
% Article template for the L'actualité économique journal  %
% -------------------------------------------------------- %
\documentclass[10pt,twoside,fleqn,english,french]{article}

% ----------------------------------- %
% Packages requis / Required packages %
% ----------------------------------- %

% Encodage des caractères en UTF-8
\usepackage[utf8]{inputenc}	
% Utilisation des polices T1		
\usepackage[T1]{fontenc}
% Citations au format auteur-année				
\usepackage{natbib}
% Internationalisation						
\usepackage{babel}
% Nécessaire pour hacker \maketitle						
\usepackage{etoolbox}
% Mise en page					
\usepackage{geometry}
% Entêtes et pieds de pages personnalisés					
\usepackage{fancyhdr}
% Titres de section personnalisés					
\usepackage{titlesec}
% Nécessaire pour hacker \maketitle (à insérer avant authblk)					
\usepackage{titling}
% Nécessaire pour hacker \maketitle					
\usepackage[blocks,affil-it]{authblk}
% Requis pour les équations
\usepackage{amsmath}
% Polices de caractères pour les maths					
\usepackage{amsfonts}
% Police Times avec symboles mathématiques
\usepackage{mathptmx}
% Nécessaire pour les graphiques et images					
\usepackage{graphicx}
% Descriptions de graphiques et tableaux personnalisées
\usepackage[format=plain,%
			labelsep=newline,%
			textfont=sc,%
			aboveskip=12pt,%
			position=top]{caption}
% Révision des manuscrits
\usepackage{changes}
			
% AUTEURS : INSÉREZ VOS PACKAGES ICI
% AUTHORS : INSERT YOUR PACKAGES HERE		

% ---------------------- %
% Mise en page / Layout  %
% ---------------------- %
\geometry{papersize={6.25in,9.5in},
		nomarginpar,
		includehead,
		nofoot,
		hdivide={0.875in,*,0.875in},
		vdivide={63pt,*,0.7917in},
		headsep=0.25in,
		headheight=9pt}					% Format de page
\setlength{\parindent}{15pt}			% Indentation des premières lignes de paragraphes
\setlength{\parskip}{6pt}				% Espacement entre les paragraphes
\setlength{\mathindent}{15pt}			% Indentation des équations
\setlength{\affilsep}{0pt}				% Espacement entre l'auteur et son affiliation

% Reformatage de la taille de caractères \normalsize
\makeatletter
\g@addto@macro\normalsize{%
	\setlength\abovedisplayskip{0pt}
	\setlength\belowdisplayskip{0pt}
	\setlength\abovedisplayshortskip{0pt}
	\setlength\belowdisplayshortskip{0pt}
}
\makeatother

% Formatage de la taille de caractères pour l'auteur
\renewcommand{\Authfont}{\fontsize{10}{12}\selectfont}

% ---------------------------------------------- %
% Personnalisation des entêtes et pieds de pages %
% ---------------------------------------------- %
\pagestyle{fancy}
\fancyhf{}
% Entêtes
\fancyhead[RO,LE]{\thepage}
\fancyhead[CE]{\fontsize{7.5}{9}\selectfont\MakeUppercase{L'Actualité économique}}
\fancyhead[CO]{\fontsize{7.5}{9}\selectfont\MakeUppercase{\AEINTtitre}}
% Pieds de pages
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\renewcommand{\footnoterule}{\noindent\rule[4pt]{48pt}{0.5pt}}

% -------------------------------------- %
% Options des packages / Package options %
% -------------------------------------- %

% caractères « et » sont les guillemets
\frenchbsetup{%
	og=«, fg=»                     
}

% Traductions françaises
\addto\captionsfrench{%
	\renewcommand{\figurename}{\MakeUppercase{Graphique}}
	\renewcommand{\tablename}{\MakeUppercase{Tableau}}
	\renewcommand{\refname}{BIBLIOGRAPHIE}
}

% Personnalisation de la section du titre de l'article
\pretitle{\vspace{-42pt}
			\AEentetePageTitre%
			\begin{center}%
			\fontsize{14}{16}\selectfont}
\posttitle{\par\vspace{24pt}%
			\end{center}}

% ------------------ %
% Hack de \maketitle %
% ------------------ %
\makeatletter
% patch \maketitle so that it doesn't center
\patchcmd{\@maketitle}{center}{flushleft}{}{}
\patchcmd{\@maketitle}{center}{flushleft}{}{}
% patch the patch by authblk so that the author block is flush left
\def\maketitle{{%
		\renewenvironment{tabular}[2][]
		{\begin{flushleft}}
			{\end{flushleft}}
		\AB@maketitle}}
\makeatother

% ----------------------------------------- %
% Commandes internes / Placeholder commands %
% ----------------------------------------- %

% Titre de l'article (pour l'entête)
\newcommand{\AEINTtitre}{}
% Volume de la revue (pour l'entête)
\newcommand{\AEINTvolume}{}
% Numéro de la revue (pour l'entête)
\newcommand{\AEINTnumero}{}
% Date de parution de la revue (pour l'entête)
\newcommand{\AEINTdate}{}

% ------------------------------------------ %
% Commandes personnalisées / Custom commands %
% ------------------------------------------ %

% Titre de l'article
\newcommand{\AEtitre}[1]{%
	\title{\MakeUppercase{#1}}%
	\renewcommand{\AEINTtitre}{#1}
}

% Volume de la revue
\newcommand{\AEvolume}[1]{%
	\renewcommand{\AEINTvolume}{#1}
}

% Numéro de la revue
\newcommand{\AEnumero}[1]{%
	\renewcommand{\AEINTnumero}{#1}
}

% Date de parution de la revue
\newcommand{\AEdateParution}[1]{%
	\renewcommand{\AEINTdate}{#1}
}

% Entête de la page titre
\newcommand{\AEentetePageTitre}{%
	\noindent{\fontsize{8}{10}\selectfont L'Actualité économique, Revue d'analyse économique, vol.~\AEINTvolume, n\textsuperscript{o}~\AEINTnumero, \AEINTdate}\\[9pt] % 9 + 6 + 16 = 31
}

% Section Introduction de l'article
\newcommand{\AEintroduction}{%
	\setcounter{secnumdepth}{0}
	\titleformat{\section}%
		{\fontsize{10}{12}\selectfont\scshape}%
		{}{0pt}%
		{}{}
	\section{Introduction}
}

% Section Conclusion de l'article
\newcommand{\AEconclusion}{%
	\setcounter{secnumdepth}{0}
	\titleformat{\section}%
	{\fontsize{10}{12}\selectfont\scshape}%
	{}{0pt}%
	{}{}
	\section{Conclusion}
}

% Sections de développement de l'article
\newcommand{\AEsectionsDeveloppement}{%
	\setcounter{secnumdepth}{3}
	\titleformat{\section}%
		{\fontsize{10}{12}\selectfont\scshape}%
		{\thesection.}{6pt}%
		{}{}
	\titleformat{\subsection}%
		{\fontsize{10}{12}\selectfont\itshape}%
		{{\normalfont\thesubsection}}{6pt}%
		{}{}
	\titleformat{\subsubsection}%
	{\fontsize{10}{12}\selectfont\itshape}%
	{{\normalfont\thesubsubsection}}{6pt}%
	{}{}
}

% Section Bibliographie de l'article
\newcommand{\AEbibliographie}{%
	\titleformat{\section}{\filcenter\scshape}{}{}{}{}
}

% Défition des réviseurs du manuscrit
\newcommand{\AEreviseur}[2]{%
	\definechangesauthor[name={#1}, color=red]{#2}
}

% --------------------------------------------------- %
% Environnements personnalisés  / Custom environments %
% --------------------------------------------------- %
	
% Résumé français
\newenvironment{AEresume}%
	{\fontsize{9}{11}\selectfont\noindent\textsc{Résumé} -- }%
	{\par}
	
% Résumé anglais
\newenvironment{AEabstract}%
	{\fontsize{9}{11}\selectfont\noindent\textsc{Abstract} -- }%
	{\par}

% ------------------------------------------- %
% Métadonnées de l'article / Article metadata %
% ------------------------------------------- %

% AUTEURS : SAISISSEZ LES INFORMATIONS CI-DESSOUS
% AUTHORS : PLEASE FILL THE INFORMATIONS BELOW

\AEtitre{Titre de l'article}
\author{Premier Auteur}
\affil{Affiliation du premier auteur}
\author{Deuxième Auteur}
\affil{Affiliation du deuxième auteur}

% PERSONNEL DE LA REVUE : SAISISSEZ LES INFORMATIONS CI-DESSOUS
% JOURNAL STAFF : PLEASE FILL THE INFORMATIONS BELOW

% Volume de la revue
\AEvolume{}
% Numéro de la revue
\AEnumero{}
% Date de parution de la revue
\AEdateParution{}
\date{} % À LAISSER VIDE! / LEAVE EMPTY!

% RÉVISEURS : SAISISSEZ VOTRE NOM ET VOS INITIALES
\AEreviseur{Donald Trump}{DT}

\begin{document}
	
	% PERSONNEL DE LA REVUE : SAISISSEZ LE NUMÉRO DE LA PREMIÈRE PAGE DE L'ARTICLE
	% JOURNAL STAFF : FILL THE ARTICLE'S FIRST PAGE NUMBER
	\setcounter{page}{3}
	
	% Génération de la section du titre de l'article
	\maketitle
	% Première page non numérotée et sans entête	
	\thispagestyle{empty}			
	
	% Résumé français de l'article
	\begin{AEresume}
		During the campaign i promised to make america great again by bringing businesses and jobs back to our country. i am very proud to see companies like chrysler moving operations from mexico to michigan where there are so many great american workers!		 
	\end{AEresume}

	% Article's english abstract
	\begin{AEabstract}
		stock market just hit another record high! jobs looking very good. great book just out "a place called heaven" by dr. robert jeffress - a wonderful man!		
	\end{AEabstract}

	% Introduction de l'article
	\AEintroduction
	
		the u.s. has gained more than 5.2 trillion dollars in stock market value since election day! also record business
		enthusiasm. the issue of kneeling has nothing to do with race. it is about respect for our country flag and national
		anthem. nfl must respect this! the fake news media will not talk about the importance of the united nations security
		council's 15-0 vote in favor of sanctions on n. korea! the democrats should be ashamed. 
		
		this is a
		disgrace! draintheswamp a working dinner tonight with prime minister abe of japan and his representatives at the winter
		white house (mar-a-lago). very good talks! even those registered to vote who are dead (and many for a long time).
		depending on results we will strengthen up voting procedures! thank you to ford for scrapping a new plant in mexico
		and creating 700 new jobs in the u.s. this is just the beginning - much more to follow.
		       	
	% Sections de développement
	\AEsectionsDeveloppement
	
		\section{Une première section}
		
		\subsection{Texte ajouté}
		
		A government shutdown will be devastating to our military...something the dems care very little about! yesterday was
		another big day for jobs and the stock market. chrysler coming back to u.s. (michigan) from mexico and many more companies
		paying out tax cut money to employees. if dems won in november market would have tanked! it was headed for disaster. on my
		way to pensacola florida. \added[id=DT]{NO COLLUSION!} see everyone soon! maga china is sending an envoy and delegation to north korea - a big move
		we'll see what happens!
		 
		\subsection{Texte supprimé}
		
		make america great again! the failing @nytimes in a story by peter baker should have mentioned the rapid terminations by
		me of tpp and the paris accord and the fast.... stock market up 5 months in a row! i will be at the @usga uswomensopen in
		bedminster nj tomorrow. big crowds expected and the women are playing great-should be very exciting! weeklyaddress?? just
		arrived in taormina with @flotus melania. g7summit usa?? the reason i am staying in bedminster n. j. a beautiful
		community is that staying in nyc is \deleted[id=DT]{much more expensive and} disruptive.
		 
		\subsection{Texte modifié}
		
		meetings! i am watching \replaced[id=DT]{@foxandfriends anchors saying that I'm a very stable genius. So true!}{the democrats trying to defend the "you can keep you doctor you can keep your plan and premiums will
		go down" obamacare lie."} thank you @usnavy! usa obamacare will explode and we will all get together and piece together a
		great healthcare plan for the people. do not worry! the fake news media is going crazy with their conspiracy theories and
		blind hatred. @msnbc and @cnn are unwatchable. @foxandfriends is great! getting ready to deliver a very important decision!
		8:00 p.m. before i or anyone saw the classified and/or highly confidential hacking intelligence report it was leaked out to
		@nbcnews. so serious! with all that congress has to work on do they really have to make the weakening of the independent
		ethics watchdog as unfair as it.
		
	% Conclusion de l'article
	\AEconclusion
	
		I will be leaving for florida today to meet with some of the bravest people on earth - but people whose lives have been
		totally shattered. am also working with congress on many fronts. congratulations to doug jones on a hard fought victory.
		the write-in votes played a very big factor but a win is a win. the people of alabama are great and the republicans will
		have another shot at this seat in a very short period of time. it never ends! we believe that every american should stand
		for the national anthem and we proudly pledge allegiance to one nation under god!
		
		the united states has been reminded time
		and again in recent years that economic security is not merely related to national security -economic security is national
		security. it is vital to our national strength. apec2017 money pouring into insurance companies profits under the guise of
		obamacare is over. they have made a fortune.dems must get smart and deal! sadly they and others are fake news and the public
		is just beginning to figure it out! congress now has 6 months to legalize daca (something the obama administration was
		unable to do). if they can't i will revisit this issue! we will remain fully engaged w/ open lines of communication as
		hurricaneharvey makes landfall. america is w/ you! @govabbott @fema @dhsgov just arrived at camp david where i am
		monitoring the path and doings of hurricane harvey (as it strengthens to a class 3).
			
	% Section bibliographie
	\AEbibliographie
	% Style bibliographique
	\bibliographystyle{francais}
	% Fichier .bib contenant les références
	\bibliography{bibliographie}
		
\end{document}