% ------------------------------------------------------ %
% Gabarit d'article pour la revue L'Actualité économique %
% ------------------------------------------------------ %
\documentclass[10pt,twoside,fleqn,english,french]{actuecon}

% ------------------------------------------------------- %
% Packages requis					 					  %
% ------------------------------------------------------- %
% La classe actuecon utilise déjà les packages suivants : %
%														  %
% - inputenc											  %
% - fontenc												  %
% - natbib												  %
% - babel												  %
% - etoolbox											  %
% - geometry											  %
% - fancyhdr											  %
% - titlesec											  %
% - titling												  %
% - authblk												  %
% - amsmath												  %
% - amsfonts											  %
% - mathptmx											  %
% - graphicx											  %
% - caption												  %
% - changes												  %
%														  %
% Il n'est pas nécessaire de les charger à nouveau.		  %
% ------------------------------------------------------- %
	
% AUTEURS : INSÉREZ VOS PACKAGES ICI

% ------------------------ %
% Métadonnées de l'article %
% ------------------------ %

% AUTEURS : SAISISSEZ LES INFORMATIONS CI-DESSOUS
% Vous pouvez insérer autant de \author et de \affil que
% ce qui est nécessaire.

\AEtitre{Manifestations d'intelligence exprimées par le Président du Monde libre}
\author{Jack Dorsey}
\affil{Twitter}
\author{Benoit Hamel}
\affil{Bibliothèque \\ HEC Montréal}

% PERSONNEL DE LA REVUE : SAISISSEZ LES INFORMATIONS CI-DESSOUS

% Volume de la revue
\AEvolume{}
% Numéro de la revue
\AEnumero{}
% Date de parution de la revue
\AEdateParution{}
\date{} % À LAISSER VIDE!

% RÉVISEURS : SAISISSEZ VOTRE NOM ET VOS INITIALES
\AEreviseur{Nom Complet}{initiales}

\begin{document}
	
	% PERSONNEL DE LA REVUE : SAISISSEZ LE NUMÉRO DE LA PREMIÈRE PAGE DE L'ARTICLE
	\setcounter{page}{3}
	
	% Génération de la section du titre de l'article
	\maketitle
	% Première page non numérotée et sans entête	
	\thispagestyle{empty}			
	
	% Résumé français de l'article
	\begin{AEresume}
		I have offered daca a wonderful deal including a doubling in the number of recipients and a twelve year pathway to
		citizenship for two reasons: (1) because the republicans want to fix a long time terrible problem. (2) to show that
		democrats do not want to solve daca only use it! 95\% of americans will pay less or at worst the same amount of taxes
		(mostly far less).	 
	\end{AEresume}

	% Article's english abstract
	\begin{AEabstract}
		the dems only want to raise your taxes! our deepest sympathies and most heartfelt prayers are with the victims of the train
		derailment in washington state. we are closely monitoring the situation and coordinating with local authorities... biggest
		tax bill and tax cuts in history just passed in the senate.
	\end{AEabstract}

	% Introduction de l'article
	\AEintroduction
	
		now these great republicans will be going for final passage. thank you to house and senate republicans for your hard work
		and commitment! our fifth 1k milestone of 2017! dow24k maga important day spent at camp david with our very talented
		generals and military leaders. many decisions made including on afghanistan. just completed call with president moon of
		south korea. very happy and impressed with 15-0 united nations vote on north korea sanctions. karen handel's opponent in
		ga06 can't even vote in the district he wants to represent.... very interesting election currently taking place in france.
		just leaving florida. big crowds of enthusiastic supporters lining the road that the fake news media refuses to mention.
		very dishonest! sen. mccain should not be talking about the success or failure of a mission to the media. only emboldens
		the enemy! he's been losing so.....
		       	
	% Sections de développement
	\AEsectionsDeveloppement
	
		\section{Une section}
		
		Thank you to sue kruczek who lost her wonderful and talented son nick to the opioid scourge for your kind words while on
		@foxandfriends. we are fighting this terrible epidemic hard - nick will not have died in vain! i want to thank my @cabinet
		for working tirelessly on behalf of our country. 2017 was a year of monumental achievement and we look forward to the year
		ahead. together we are delivering results and making america great again! just landed in the philippines after a great day
		of meetings and events in hanoi vietnam! after strict consultation with general kelly the cia and other agencies i will be
		releasing all jfkfiles other than the names and...
		
		good luck to @joy\_villa on her decision to enter the wonderful world of
		politics. she has many fans! republicans are going for the big budget approval today first step toward massive tax cuts. i
		think we have the votes but who knows? wow! a great day in puerto rico yesterday. while some of the news coverage is fake
		most showed great warmth and friendship. even usain bolt from jamaica one of the greatest runners and athletes of all time
		showed respect for our national anthem! ???? 
		
		on behalf of all americans i want to wish jewish families many blessings in
		the new year. just arrived in youngstown ohio with @flotus melania! makeamericagreatagain??? the united states made some of
		the worst trade deals in world history.why should we continue these deals with countries that do not help us? really great
		numbers on jobs and the economy! things are starting to kick in now and we have just begun! don't like steel and aluminum
		dumping! the u.s. once again condemns the brutality of the north korean regime as we mourn its latest victim.
		
		\subsection{Une sous-section}
		
		video: ....because he doesn't live there! he wants to raise taxes and kill healthcare. on tuesday votekarenhandel. caught he
		cried like a baby and begged for forgiveness...and now he is judge and jury. he should be the one who is investigated for his
		acts. death spiral!'aetna will exit obamacare markets in va in 2018 citing expected losses on indv plans this year' the two
		fake news polls released yesterday abc and nbc while containing some very positive info were totally wrong in general e.
		watch! 
		
		today on earth day we celebrate our beautiful forests lakes and land. we stand committed to preserving the natural
		beauty of our nation. judge gorsuch will be sworn in at the rose garden of the white house on monday at 11:00 a.m. he will
		be a great justice. very proud of him! great meeting with a wonderful woman today former secretary of state condoleezza
		rice! usa?? watch @judgejeanine on @foxnews tonight at 9:00 p.m. find the leakers within the fbi itself. classified
		information is being given to media that could have a devastating effect on u.s. 
		
		find now the fbi is totally unable to stop
		the national security "leakers" that have permeated our government for a long time. they can't even...... iran was on its
		last legs and ready to collapse until the u.s. came along and gave it a life-line in the form of the iran deal: \$150
		billion what are hillary clinton's people complaining about with respect to the f.b.i. based on the information they had
		she should never..... 'small business optimism soars after trump election' things they did and said (like giving the
		questions to the debate to h). a total double standard! media as usual gave them a pass..
						 
		\subsubsection{Une sous-sous-section}
		
		For those asking the republicans only have 51 votes in the senate and they need 60. that is why we need to win more
		republicans in 2018 election! we can then be even tougher on crime (and border) and even better to our military and veterans!
		small business poll has highest approval numbers in the polls history. all business is just at the beginning of something
		really special! 
		
		it was an honor to welcome republican and democratic members of the senate finance committee to the
		@whitehouse today. taxreform it is about time that roger goodell of the nfl is finally demanding that all players stand
		for our great national anthem-respect our country can't believe i finally got a good story in the @washingtonpost. it
		discusses the enthusiasm of "trump" voters through campaign.... going to the white house is considered a great honor for a
		championship team.
		
		stephen curry is hesitatingtherefore invitation is withdrawn! the nra strongly endorses luther strange
		for senator of alabama.that means all gun owners should vote for big luther. he won't let you down! bernie sanders is
		pushing hard for a single payer healthcare plan - a curse on the u.s. and its people... .@chuckgrassley - got your message
		loud and clear. we have fantastic people on the ground got there long before harvey. so far so good! thank you west
		virginia! all across the country americans of every kind are coming together w/one simple goal: to make america great
		again! stock market could hit all-time high (again) 22000 today. was 18000 only 6 months ago on election day.
		
	% Conclusion de l'article
	\AEconclusion
	
		mainstream media seldom mentions! will be traveling to the great state of ohio tonight. big crowd expected. see you there! stock market hits another high with spirit and enthusiasm so positive. jobs outlook looking very good! maga?? i strongly pressed president putin twice about russian meddling in our election. he vehemently denied it. i've already given my opinion..... the failing @nytimes writes false story after false story about me. they don't even call to verify the facts of a story. a fake news joke! ....
		
		getting great border security and healthcare. voteralphnorman tomorrow! camp david is a very special place. an honor to have spent the weekend there. military runs it so well and are so proud of what they do! congratulations to @foxandfriends on its unbelievable ratings hike. i want to help our miners while the democrats are blocking their healthcare. since november 8th election day the stock market has posted \$3.2 trillion in gains and consumer confidence is at a 15 year high. jobs! congratulations to our new national security advisor general h.r. mcmaster. 
							
	% Section bibliographie
	\AEbibliographie
	\nocite{*}
	% Style bibliographique
	\bibliographystyle{econometrica}
	% Fichier .bib contenant les références
	\bibliography{bibliographie}
		
\end{document}